---
title: "Exercise_1"
output: html_document
date: "2024-10-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##*Exercise 1*
1. A developer creates a new GitHub repository, which contains an Rmarkdown file that has an R code chunk defining a function with a single argument `data`, that takes a dataset and performs some input transformation on it. This transformation can be as simple or complex as you like, but should work on at least one dataset (either a built-in R dataset, or one provided by you in the public repository). The function should return the transformed data.
2. The developer knits the Rmarkdown file, which generates an HTML file with the function inside a code chunk and the output of the function after running it on the dataset. The developer includes this knitted HTML file in the repository.
```{r}
#Loading libraries
library(tidyverse)
#The datasets library is used for this exercise, with the iris dataset  for the following exercise
library(datasets)
head(iris)

#Rename the dataset from iris to 'data'
data<- iris
head(data)

#Round values for the Sepal Length
data$Sepal.Length<-round(data$Sepal.Length,0)
head(data)

```

3. The developer wishes to a second function that does a different transformation, but also takes a single argument `data` (a dataset) and returns a transformed dataset. To preserve the integrity of the main branch, they add this functionality in a new branch called `dev`, which they do *not* immediately merge into main.

```{r}
data$Petal.Area <- data$Petal.Length*data$Petal.Width
data_new <- data
head(data_new)

```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
